\documentclass[12pt]{article}%[a4paper,10pt]

% A Few Useful Packages
\usepackage{marvosym,fontspec,titlesec,charter}
\usepackage{xunicode,xltxtra,url,parskip}
\RequirePackage{color,graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[margin=0.8in]{geometry}

% Setup hyperref package, and colours for links
\usepackage{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}

\usepackage{fancyhdr}\pagestyle{fancy}
\renewcommand{\headrulewidth}{0pt}% Default header rule
\renewcommand{\footrulewidth}{0pt}% No footer rule
\fancyhf{}% Clear header/footer
\fancypagestyle{plain}{
  \renewcommand{\headrulewidth}{0pt}% No header rule
  \renewcommand{\footrulewidth}{0pt}% Default footer rule
  \fancyhf{}% Clear header/footer
}
\AtBeginDocument{\thispagestyle{plain}}

\setlength{\parindent}{0pt}
\setlength{\parskip}{.5\baselineskip plus 1pt minus 1pt}

\setlength{\headheight}{0pt}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% FONTS
\defaultfontfeatures{Mapping=tex-text}
\setmainfont[
    Path = ../fonts/,
    SmallCapsFont = Fontin-SmallCaps.otf,
    BoldFont = Fontin-Bold.otf,
    ItalicFont = Fontin-Italic.otf
]
% A font by Jos Buivenga (exljbris) -> www.exljbris.com
{Fontin.otf}
%%%

%%%%%%%%%%
% Colors %
%%%%%%%%%%

\RequirePackage{xcolor}

\definecolor{white}{RGB}{255,255,255}
\definecolor{gray}{HTML}{4D4D4D}
\definecolor{lightgray}{HTML}{D3D3D3}
\definecolor{darkgrey}{HTML}{404040}


\RequirePackage{enumitem,wasysym} %  https://tex.stackexchange.com/questions/85335/how-to-change-dot-spacing-in-dotfill
\newcommand{\tick}{\dotfill\(\ocircle\)}
\newcommand{\blue}[1]{\textcolor{blue!70!white}{#1}}
\newcommand{\red}[1]{\textcolor{red}{#1}}
\newcommand{\green}[1]{\textcolor{green!70!black}{#1}}
\newcommand{\quant}[1]{\red{#1}\tick}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%--------------------BEGIN DOCUMENT----------------------
\begin{document}

% \vspace*{\baselineskip}

{\LARGE \blue{Mango \& Chicken Casserole} \hfill\normalsize Tana Ramsay, 3-4 people}

\vspace{-\baselineskip}\hrulefill

\vspace{-0.5\baselineskip}\hfill {\footnotesize Prep \green{25 minutes}, Cook \green{2 hours}}

\subsection*{Ingredients}

\begin{itemize}[nolistsep]
    \item Olive Oil --- \red{2 tablespoons} \tick
    \item Butter --- \red{2 tablespoons} \tick
    \item Chicken Breast --- \red{1kg, skinless and boneless} \tick
    \item Large Onion --- \red{2} \tick
    \item Large Mango --- \red{2, peeled and diced} \tick
    \item Chicken Stock --- \red{400ml} \tick
    \item Lemon Zest --- \red{1 whole lemon} \tick
    \item Ground Cinnamon --- \red{1 teaspoon} \tick
    \item Ground Coriander --- \red{1 teaspoon} \tick
    \item Single Cream --- \red{250ml} \tick
    \item Water --- \red{1 tablespoon} \tick
    \item Lemon Juice --- \red{1 whole lemon} \tick
    \item Flour --- \red{2 teaspoons} \tick
\end{itemize}

Serve dish with plain rice.

\subsection*{Instructions}

Preheat the oven to 190\(^{\circ}\)C.

\begin{enumerate}
    \item Brown the \blue{chicken} pieces, \blue{oil}, and \blue{butter} in a frying pan, and then transfer to a casserole dish.%\tick
    \item Fry the \blue{onion} until soft and add to the chicken.%\tick
    \item Gently fry \blue{mango} pieces over a low heat for about 4 minutes, turning frequently.%\tick
    \item Stir in the \blue{lemon zest} (not juice), \blue{coriander}, \blue{cinnamon}, and \blue{chicken stock}, bring to a boil, and then pour over the chicken. Cover the dish and bake in the over for 1 hour.%\tick
    \item Pour everything from the casserole dish into the frying pan. Take the chicken pieces out and put back into the casserole dish and cover.
    \item Put the \blue{rice} on and cook as directed.%\tick
    \item Turn up the heat and bring to the boil, letting it reduce down and thicken.%\tick
    \item Turn down the heat and stir in the \blue{cream}.%\tick
    \item Mix the \blue{flour}, \blue{lemon juice}, and \blue{water} and beat into the mixture.%\tick
    \item Simmer together for a few minutes, and then pour over the chicken and serve on a bed of rice.%\tick
\end{enumerate}

\end{document}
