\documentclass[12pt]{article}%[a4paper,10pt]

%----------Useful Packages----------%
\usepackage{marvosym,fontspec,titlesec,charter}
\RequirePackage{xcolor,graphicx}
\usepackage[margin=0.8in]{geometry}

%----------Page Setup----------%

\usepackage{fancyhdr}\pagestyle{fancy}
\renewcommand{\headrulewidth}{0pt}% Default header rule
\renewcommand{\footrulewidth}{0pt}% No footer rule
\fancyhf{}% Clear header/footer
\fancypagestyle{plain}{
  \renewcommand{\headrulewidth}{0pt}% No header rule
  \renewcommand{\footrulewidth}{0pt}% Default footer rule
  \fancyhf{}% Clear header/footer
}
\AtBeginDocument{\thispagestyle{plain}}

\setlength{\parindent}{0pt}
\setlength{\parskip}{.5\baselineskip plus 1pt minus 1pt}

\setlength{\headheight}{0pt}

%----------Fonts----------%

\defaultfontfeatures{Mapping=tex-text}
\setmainfont[
    Path = ../fonts/,
    SmallCapsFont = Fontin-SmallCaps.otf,
    BoldFont = Fontin-Bold.otf,
    ItalicFont = Fontin-Italic.otf
]
% A font by Jos Buivenga (exljbris) -> www.exljbris.com
{Fontin.otf}

%----------Extras----------%

\RequirePackage{enumitem,wasysym} %  https://tex.stackexchange.com/questions/85335/how-to-change-dot-spacing-in-dotfill
\newcommand{\tick}{\dotfill\(\ocircle\)}
\newcommand{\blue}[1]{\textcolor{blue!70!white}{#1}}
\newcommand{\red}[1]{\textcolor{red}{#1}}
\newcommand{\quant}[1]{\red{#1}\tick}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%--------------------BEGIN DOCUMENT----------------------
\begin{document}

% \hrulefill
\vspace*{\baselineskip}

{\LARGE \blue{Coconut Mousse}}% \hfill\normalsize [Quantity]}

\vspace{-\baselineskip}\hrulefill

\subsection*{Ingredients}

\begin{itemize}[nolistsep]
    \item Eggs --- \quant{4, separated}
    \item Caster Sugar --- \quant{4 ounces}
    \item Creamed Coconut --- \quant{2 ounces}
    \item Cornflour --- \quant{1 ounce}
    \item Sachet Gelatine --- \quant{1 sachet}
    \item Desiccated Coconut --- \quant{4 ounces}
    \item Double Cream --- \quant{10 fluid ounces}
    \item Milk --- \quant{1 pint}
\end{itemize}

Serve dish with cold fruit sauce or stewed fruits.

\subsection*{Instructions}

\begin{enumerate}
    \item Put the \blue{milk} and \blue{creamed coconut} in a thick-based saucepan and bring to the boil stirring regularly. Meanwhile put the \blue{egg yolks} in a large bowl, add the \blue{caster sugar} and \blue{cornflour} and mix well.
    \item Pour the boiling milk on the egg yolks and mix well.
    \item Clean the saucepan and pour the mixture back in, return to the heat and stir over a gentle heat until the mixture boils.
    \item Return the mixture to the bowl. Dissolve the \blue{gelatine} in a little hot water and add to the mixture. Stir well.
    \item Leave to cool until almost at setting point, stirring occasionally.
    \item Whip the \blue{cream} and fold into the mixture. Whisk the \blue{egg whites} and fold in.\footnote{If you are concerned with using uncooked egg whites, then do not use them in the mousse. Instead, mix \blue{dried egg white} to the equivalent of 4 egg whites made as directed on the packet. Whisk and fold into the mousse. (Supercook make dried pasteurised egg white and it is available at most supermarkets. You can use the egg whites to make meringues or cakes where they will be fully cooked.)}
    \item Leave the mousse in the fridge until set.
\end{enumerate}

\end{document}
