\documentclass[12pt]{article}%[a4paper,10pt]

%----------Useful Packages----------%
\usepackage{marvosym,fontspec,titlesec,charter}
\RequirePackage{xcolor,graphicx}
\usepackage[margin=0.8in]{geometry}

%----------Page Setup----------%

\usepackage{fancyhdr}\pagestyle{fancy}
\renewcommand{\headrulewidth}{0pt}% Default header rule
\renewcommand{\footrulewidth}{0pt}% No footer rule
\fancyhf{}% Clear header/footer
\fancypagestyle{plain}{
  \renewcommand{\headrulewidth}{0pt}% No header rule
  \renewcommand{\footrulewidth}{0pt}% Default footer rule
  \fancyhf{}% Clear header/footer
}
\AtBeginDocument{\thispagestyle{plain}}

\setlength{\parindent}{0pt}
\setlength{\parskip}{.5\baselineskip plus 1pt minus 1pt}

\setlength{\headheight}{0pt}

%----------Fonts----------%

\defaultfontfeatures{Mapping=tex-text}
\setmainfont[
    Path = ../fonts/,
    SmallCapsFont = Fontin-SmallCaps.otf,
    BoldFont = Fontin-Bold.otf,
    ItalicFont = Fontin-Italic.otf
]
% A font by Jos Buivenga (exljbris) -> www.exljbris.com
{Fontin.otf}

%----------Extras----------%

\RequirePackage{enumitem,wasysym} %  https://tex.stackexchange.com/questions/85335/how-to-change-dot-spacing-in-dotfill
\newcommand{\tick}{\dotfill\(\ocircle\)}
\newcommand{\blue}[1]{\textcolor{blue!70!white}{#1}}
\newcommand{\red}[1]{\textcolor{red}{#1}}
\newcommand{\quant}[1]{\red{#1}\tick}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%--------------------BEGIN DOCUMENT----------------------
\begin{document}

% \hrulefill
\vspace*{\baselineskip}

{\LARGE \blue{Pancakes} \hfill\normalsize 6 Pancakes}

\vspace{-\baselineskip}\hrulefill

\subsection*{Ingredients}

\begin{itemize}[nolistsep]
    \item Self-raising Flour --- \quant{135g (4\(^{3}\!/\!_{4}\) ounces)}
    \item Caster Sugar --- \quant{2 Tablespoons}
    \item Milk --- \quant{130ml (4\(^{1}\!/\!_{2}\) fluid ounces)}
    \item Large Egg --- \quant{1, lightly beaten}
    \item Butter --- \quant{2 Tablespoons, melted}
\end{itemize}

One may add \blue{raspberries} or \blue{chocolate chips} for extra sweetness. Serve dish with maple syrup.

\subsection*{Instructions}

\begin{enumerate}
    \item In a small bowl, melt the \blue{butter} and leave to cool.
    \item Sift the \blue{flour} and \blue{caster sugar} into a big bowl and combine.
    \item In a separate bowl, lightly beat the \blue{egg}. Add the \blue{milk} and combine, and then add the butter and whisk.
    \item Pour the wet ingredients into the dry ones, mixing until smooth and thick (add more flour if necessary).
    \item Add the \blue{raspberries} or \blue{chocolate chips} and mix until combined.
    \item Put a small pan on a medium--low heat with a small amount of butter. When hot, add a large spoonful of batter using a ladle (or large spoon) to the pan. Cover and cook, flipping the pancake once when bubbles form on the surface.
\end{enumerate}

\end{document}
